\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry}

\firstname{Guanli}
\familyname{Liu}
\address{Spencer St.}{Melbourne, VIC, 3000}
\phone{0450075953}
\email{liuguanli22@gmail.com}

\begin{document}
% \recipient{Hiring Committee}{CSIRO}
\recipient{Hiring Committee}{}
\date{\today}
\opening{Dear Renata,}
\closing{Sincerely,}
\makelettertitle

I am writing to apply for the position: Postdoctoral Research Fellow in AI-driven Databases.

As a newly minted PhD graduate from the University of Melbourne, specialising in spatial data indexing and spatial query processing, I am excited about leveraging my skills in a practical, real-world environment. My solid grounding in AI, machine learning and data analysis further enhances my readiness for the role.

In my current role as a Data Scientist at nftDb, I've managed large datasets and utilized my robust programming skills (Python, Java, C++), as well as tools like Google BigQuery, to extract meaningful insights. I am confident in managing and processing large data volumes, including spatial data, and am familiar with Google Cloud Platform's distributed computing environments.

My work experience prior to my PhD, as a Software Engineer at Baidu, has provided me with a solid foundation in creating practical software solutions and fostering strong teamwork. Additionally, I gained valuable experience in teaching and collaborating with others during my tenure as a tutor at the University of Melbourne, where I guided students in leveraging GitHub for version control.

My published work in spatial data processing, all accepted by A* rated conferences and journals, along with the hands-on experience from my academic and professional roles, positions me uniquely for the significant contributions I can make to the National Bushfire Intelligence Capability (NBIC) projects and other initiatives within the CSIRO Environment Business Unit.

I look forward to the opportunity to work and interact with the highly skilled and diverse team at CSIRO. I am particularly interested in continuous learning and contributing to innovation within your esteemed organization.

Thank you for considering my application. I am eager to further discuss how my background and skills align with your team's needs.

\vspace{1cm}

Sincerely,

\vspace{0.5cm}

Guanli

\end{document}
