\documentclass{resume}
\usepackage{xcolor}
% \usepackage[hidelinks]{hyperref}

\begin{document}
\pagenumbering{gobble}

\name{Guanli Liu}

\basicInfo{
  \email{guanlil1@unimelb.edu.au} \textperiodcentered\
  \linkedin[Guanli Liu]{https://www.linkedin.com/in/guanli-liu-11353058/} \textperiodcentered\
  \github[https://github.com/Liuguanli]{https://github.com/Liuguanli}
}

% -------------------------
% Profile
% -------------------------
\section{\faUser\ \textbf{Profile}}
Data Scientist and Postdoctoral Research Fellow with expertise in \textbf{machine learning for databases}, large-scale data analytics, and intelligent query optimization.  
Over 7 years of experience building and benchmarking AI-driven data systems — from model-based indexing in \textbf{PostgreSQL} to \textbf{Python/BigQuery} pipelines for production data platforms.  
Combines strong algorithmic understanding with practical engineering in \textbf{PyTorch}, \textbf{dbt}, and \textbf{GCP}.

% -------------------------
% Education
% -------------------------
\section{\faGraduationCap\ \textbf{Education}}
\datedsubsection{\textbf{PhD in Computer Science}, \textit{The University of Melbourne}, Australia}{2019 -- 2023}
Research: Learned spatial indexes, reinforcement learning for query optimization, and AI-augmented database systems.

\datedsubsection{\textbf{M.S. in Computer Technology}, \textit{Northeastern University}, China (Top 10\%)}{2013 -- 2015}
\datedsubsection{\textbf{B.Eng. in Software Engineering}, \textit{Northeastern University}, China (Top 20\%)}{2009 -- 2013}

% -------------------------
% Experience
% -------------------------
\section{\faUsers\ \textbf{Professional Experience}}

\datedsubsection{\textbf{Postdoctoral Research Fellow}, \textbf{The University of Melbourne}}{Feb. 2024 -- Present}
\begin{itemize}
  \item Designed \textbf{RL-enhanced spatial index benchmark} in \textbf{PostgreSQL}, evaluating adaptive query strategies across 10B+ records.  
  \item Built \textbf{AI-driven cost models} and learned estimators to optimize analytical workloads; integrated RL modules with DB optimizer hooks.  
  \item Collaborated with teams at \textbf{Aalborg University} and \textbf{RMIT}, producing accepted papers at \textit{VLDB 2024} and \textit{ICDE 2026}.  
  \item Supervised master’s students on applied ML topics (LLM-augmented spatial queries, vector embeddings).
\end{itemize}

\datedsubsection{\textbf{Data Scientist}, \textbf{\href{https://nftdb.ai/}{nftDb \faExternalLink}}, Australia}{Feb. 2023 -- Feb. 2024}
\begin{itemize}
  \item Engineered data pipelines with \textbf{Python, dbt, and BigQuery} processing \textbf{200M+ NFT transactions}.  
  \item Developed wallet clustering and ranking algorithms using \textbf{PageRank} and \textbf{unsupervised learning}, improving fraud detection by 25\%.  
  \item Designed metrics dashboards and data services on \href{https://databeast.xyz/}{\textbf{Databeast}} for real-time NFT analytics.
\end{itemize}

\datedsubsection{\textbf{Software Engineer}, \textbf{Baidu}, China}{Jul. 2015 -- Aug. 2017}
\begin{itemize}
  \item Contributed to Baidu’s enterprise IM system \href{https://infoflow.baidu.com/}{\textbf{Infoflow}}, serving millions of active users.  
  \item Implemented message protocols and voice-assistant modules in \textbf{Java/Android}.  
  \item Improved backend query performance by 20\% via indexing and caching optimizations.
\end{itemize}

% -------------------------
% Selected Projects
% -------------------------
\section{\faDatabase\ \textbf{Selected Projects}}
\begin{itemize}
  \item \textbf{RL-Enhanced Spatial Index Benchmark:} Open-source benchmark comparing learned, traditional, and RL-optimized indexes in PostgreSQL.  
        \href{https://github.com/Liuguanli/rl_spatial_benchmark}{\textcolor{blue}{\texttt{[Code]}}}
  \item \textbf{LLM-Augmented Query Optimizer:} Built prototype integrating GPT reasoning with database query plans for adaptive optimization.  
  \item \textbf{NFT Market Analytics Platform:} End-to-end Python/dbt pipelines and clustering-based behavioral modeling for token analytics.  
\end{itemize}

% -------------------------
% Publications (top-tier)
% -------------------------
\section{\faFile\ \textbf{Selected Publications}}
\begin{itemize}
  \item \textbf{Guanli Liu}, Renata Borovica-Gajic, Hai Lan, Zhifeng Bao.  
``Benchmarking RL-Enhanced Spatial Indices Against Traditional, Advanced, and Learned Counterparts.''  
\textit{ICDE}, 2026. 

 \item \textbf{Guanli Liu}, Lars Kulik, Christian S. Jensen, Tianyi Li, Renata Borovica-Gajic, Jianzhong Qi.  
  ``Efficient Cost Modeling of Space-filling Curves." \textit{VLDB}, 2025.  

  % \item \textbf{Guanli Liu}, Jianzhong Qi, Lars Kulik, Kazuya Soga, Renata Borovica-Gajic, Benjamin I. P. Rubinstein.  
  % ``Efficient Index Learning via Model Reuse and Fine-tuning." \textit{ICDEW}, 2023.  
  % Explores transfer learning for learned indexes, reducing training costs while maintaining high accuracy.

  \item \textbf{Guanli Liu}, Jianzhong Qi, Christian S. Jensen, James Bailey, Lars Kulik.  
  ``Efficiently Learning Spatial Indices." \textit{ICDE}, 2023.  
\end{itemize}

% -------------------------
% Technical Skills
% -------------------------
\section{\faCogs\ \textbf{Technical Skills}}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Languages:} Python, SQL, Java, C++
  \item \textbf{Data \& ML:} Pandas, NumPy, Scikit-learn, PyTorch, TensorFlow, XGBoost
  \item \textbf{Big Data:} PostgreSQL, BigQuery, Spark, dbt, Airflow
  \item \textbf{Cloud/DevOps:} Google Cloud Platform (GCP), Docker, Linux, Git
  \item \textbf{Visualization:} Matplotlib, Seaborn, Tableau
\end{itemize}

\end{document}
