% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{xcolor}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Guanli Liu}

\basicInfo{
  \email{liuguanli22@gmail.com} \textperiodcentered\ 
  \phone{(+61) 450075953} \textperiodcentered\ 
%  \linkedin[Guanli Liu]{https://www.linkedin.com/in/guanli-liu-11353058/} \textperiodcentered\ 
  \github[https://github.com/Liuguanli]{https://github.com/Liuguanli}
  }

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming languages: Java, Python, C++
  \item Machine learning tools: TensorFlow, PyTorch, TorchLib, Scikit-learn, Weka,
  \item Research interests: AI for DB, Learned index, Spatial index, Spatial data management
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The University of Melbourne}, Melbourne, Australia}{Jun. 2019 -- Present (expected \textbf{Jul. 2023})} 
\textit{PhD Candidate} in Computing and Information System (GPA: H1)
\datedsubsection{\textbf{Northeastern University}, Shenyang, China}{Aug. 2013 -- Jun. 2015}
\textit{M.S.} in Computer Technology (GPA: 3.5 / Top 10\%)
\datedsubsection{\textbf{Northeastern University}, Shenyang, China}{Aug. 2009 -- Jun. 2013}
\textit{B.Eng.} in Software Engineering (GPA: 3.4 / Top 20\%)



\section{\faUsers\ Experience}

\datedsubsection{\textbf{The University of Melbourne}, Victoria, Australia}{Aug. 2019 -- Present}
\role{Tutor}{Comp90018 (Mobile Computing) \& Comp90041 (Programming and Software Development)} 
%Duties: 
\begin{itemize}
  \item \textbf{Android} (Comp90018) and \textbf{Java} (Comp90041) demonstration for about 100 students each term
  \item Project guidance and assignment marking for each team (5 or 6 students)
\end{itemize}

\datedsubsection{\textbf{Baidu Inc.}, Beijing, China}{Jul. 2015 -- Aug. 2017}
\role{Researcher and Developer}{Android Development (\textbf{Java})}
Worked in an Android Development group focusing on Instant Messaging (IM) software development, which is part of an enterprise intelligent work platform \href{https://infoflow.baidu.com/}{[\textbf{infoflow}]} for all employees in Baidu and cooperative enterprises.
%We pay attention to team work and each single task is finished with PM, UI, UE, QA and interior code review. 
Key contributions are as follows:

\begin{itemize}
  \item Designed new message protocols, e.g., Recall message, Delete message, Red pocket Message, etc.
  \item Designed Voice Assistant module by voice recognition SDK to send message, order meeting room, etc.
  \item Optimised the database retrieval efficiency by about 20\% by optimising database table index.
  \item Optimised application centre UI with flexible configuration by new widgets.
  \item Improved all message module development efficiency by using design patterns, e.g., Builder.
  \item Analysed, fixed, and documented tough bugs.
\end{itemize}

\section{\faFilesO\ Publications}
\begin{itemize}
 \item Guanli Liu, Lars Kulik, Xingjun Ma, Jianzhong Qi. A Lazy Approach for Efficient Index Learning. arXiv preprint arXiv:2102.08081. \href{https://github.com/Liuguanli/ModelReuse}{[\textbf{source code}] (\textbf{C++})} 
 
  \item Jianzhong Qi (supervisor), Guanli Liu, Christian S. Jensen, and Lars Kulik. Effectively Learning Spatial Indices. PVLDB, 13(11): 2341-2354, 2020.  \href{https://github.com/Liuguanli/RSMI}{[\textbf{source code}] (\textbf{C++})}

  \item Yu Gu (supervisor), Guanli Liu, Jianzhong Qi, Hongfei Xu, Ge Yu, and Rui Zhang. The Moving K Diversified Nearest Neighbor Query. TKDE, 28(10): 2778-2792, 2016.
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}




\section{\faHeartO\ Honors and Awards}
\datedline{Yearly performance appraisal in Baidu \textit{Top 20\%}}{2016}
\datedline{Outstanding master student \textit{Top 5\%}}{2014}
\datedline{\textit{\nth{3} Prize} prize of American college students' mathematical modelling contest}{2011}
\datedline{\textit{\nth{3} Prize} prize of Google Android application development in China}{2011}


%\section{\faInfo\ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
  %\item GitHub: https://github.com/Liuguanli
  %\item Languages: English - Fluent, Mandarin - Native speaker
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
