% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{xcolor}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Guanli Liu}

\basicInfo{
  \email{liuguanli22@gmail.com} \textperiodcentered\ 
  \phone{(+61) 450075953} \textperiodcentered\ 
  \linkedin[Guanli Liu]{https://www.linkedin.com/in/guanli-liu-11353058/} \textperiodcentered\ 
  \github[GitHub]{https://github.com/Liuguanli}}

{\color{red}
\section{\faPencilSquare\ Summary}
I am a third-year PhD student at the University of Melbourne. My research interest is using machine learning
technology to build database indices, e.g., B-trees and R-trees. Before UoM, I was a senior
researcher and developer in Baidu Inc. in Beijing, China.
}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java, Python, C++, Kotlin, SQL
  \item Development: Java Web, Android
  \item Machine Learning: TensorFlow, PyTorch, TorchLib, Scikit-learn, Weka,
  \item Methodologies: Agile, Scrum
  \item Research: LaTex, Spatial Database, Learned index

  
%    \item Development: Java Web, Java, Android, SQL, LaTex, TensorFlow, PyTorch
%  \item Development: Java Web, Java, Android, SQL, LaTex, TensorFlow, PyTorch
\end{itemize}

\section{\faUsers\ Experience}

\datedsubsection{\textbf{Baidu Inc.} Beijing, China}{Jul. 2015 -- Aug. 2017}
\role{Senior Researcher and Developer}{Android developer}
Our team develops enterprise intelligent work platform \href{https://infoflow.baidu.com/}{[\textbf{infoflow}]}, which supports Desktop, iOS, and Android. I worked in an Android Development group with around ten engineers, focusing on Instant Messaging (IM) development.  We pay attention to team work and each single task is finished with PM, UI, UE, QA and interior code review. Key contributions are as follows:
\begin{itemize}
  \item Message design: protocol design, Recall message, Delete message, Red pocket Message, etc
  \item Heartbeat mechanism:
  \item Voice assistant: Voice recognition SDK integration, send message, order meeting room, etc
  \item Application centre: Configure and manage enterprise applications
\end{itemize}

\datedsubsection{\textbf{The University of Melbourne} Victoria, Australia}{Aug. 2019 -- Present}
\role{Tutor}{Comp90018 (Mobile Computing)}
%Duties: 
\begin{itemize}
  \item Android development introduction and project guidance
  \item Assignment marking and feedback
\end{itemize}

\role{Tutor}{Comp90041 (Programming and Software Development)}
%Duties:
\begin{itemize}
  \item Java development introduction and questions demonstration
    \item Assignment marking and feedback
\end{itemize}

\datedsubsection{\textbf{Neusoft } Shenyang, China}{Jun. 2012 -- Sep. 2012}
\role{Software Engineer (internship)}{Java Web development}

\begin{itemize}
  \item Building a logistics management system with Java EE  (Struts + Spring + Hibernate)
\end{itemize}


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The University of Melbourne}, Melbourne, Australia}{2019 -- Present}
\textit{PhD Candidate} in Computing and Information System, expected December 2022
\datedsubsection{\textbf{Northeastern University}, Shenyang, China}{2013 -- 2015}
\textit{M.S.} in Computer Technology
\datedsubsection{\textbf{Northeastern University}, Shenyang, China}{2009 -- 2013}
\textit{B.S.} in Software Engineering
  

\section{\faFilesO\ Published Papers}
\begin{itemize}
 \item Guanli Liu, Lars Kulik, Xingjun Ma, Jianzhong Qi. A Lazy Approach for Efficient Index Learning. arXiv preprint arXiv:2102.08081. \href{https://github.com/Liuguanli/ModelReuse}{[\textbf{source code}]} 
 
  \item Jianzhong Qi (supervisor), Guanli Liu, Christian S. Jensen, and Lars Kulik. Effectively Learning Spatial Indices. PVLDB, 13(11): 2341-2354, 2020.  \href{https://github.com/Liuguanli/RSMI}{[\textbf{source code}]}

  \item Yu Gu (supervisor), Guanli Liu, Jianzhong Qi, Hongfei Xu, Ge Yu, and Rui Zhang. The Moving K Diversified Nearest Neighbor Query. TKDE, 28(10): 2778-2792, 2016.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}



\section{\faHeartO\ Honors and Awards}
\datedline{Performance appraisal in Baidu \textit{Top 20\%}}{2016}
\datedline{Outstanding master student \textit{Top 5\%}}{2014}
\datedline{\textit{\nth{3} Prize} prize of American college students' mathematical modelling contest}{2011}
\datedline{\textit{\nth{3} Prize} prize of Google Android application development in China}{2011}


%\section{\faInfo\ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
  %\item GitHub: https://github.com/Liuguanli
  %\item Languages: English - Fluent, Mandarin - Native speaker
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
